Formalizing Stack Safety as a Security Property

### 2022-09-06 submission5/onlyformalism.tex
Activation ids

We begin with a RISC-V-like machine enhanced with PIPE, a tag-based reference
monitory. We extend this machine with a {\it security overlay semantics}:
a semantics in which calls, returns, and other operations of interest are condensed
into atomic {\it macro-instructions}, which update an additional security context.
As opposed to a fully-abstract overlay semantics, in which the semantics is safe
by construction and compilation to an enforcement mechanism must be proved fully abstract,
our machine's semantics are not safe unless the tag policy is correctly
instantiated, but the security context informs trace properties that
must hold under a policy for that policy to be considered valid.

The underlying machine is a standard RISC-V ISA as modeled in [MIT-RISCV].
Our overlay semantics provide macro-instructions for the following code features:
\begin{itemize}
\item Function calls and returns, with caller- and callee-saved registers according
  to the RISC-V ABI
\item Arguments passed by reference
\item Exceptions
\item Tail-call Elimination
\end{itemize}

\paragraph*{What is a ``call''?} Some ISAs have a single ``call''
instruction that does all the required manipulation of the program counter
(\(\PCname\)) and stack pointer; others perform a series of instructions
whose constituent opcodes may be used in some places for other purposes.
Our RISC-V machine is the latter, so calls must be explicitly designated
as such by the compiler, by identifying them as macro-instructions.
The same goes for other operations, such as exceptions.
Macro-instructions connect the enforcement mechanism to the property: we don't
expect the enforcement mechanism to provide any guarantees for code sequences
that resemble calls or returns, but which are not macro-instructions.

Because macro-instructions must be generated by the compiler, they only
carry data that can be known by the compiler at compile-time. For example,
the \(\mathbf{call}\) macro-instruction identifies the register \(r_{target}\) containing
the address of the function to be called, as well as the registers that hold arguments.

%\paragraph*{Enforcement Model and Properties}

%A machine state consists of the standard addresses and registers, as well as
%additional policy state used by the enforcement mechanism. Our properties
%refer only to addresses and registers; they do not constrain the behavior
%of policy state. We model an execution step as a partial function on states:
%when the machine does not step from a given state, this
%is a {\em failstop}, halting the program before it can perform an
%action that would violate the security property.
%our properties are therefore naturally \emph{termination insensitive.}

@@

\section{The Basic Machine}

@@

Collectively addresses and registers are {\em state elements} \(\component\)
in the set \(\COMPONENTS ::= \WORDS + \REGS\).
%
A {\em machine state} \(\mach \in \MACHS\) is a type that exposes a mapping
\(\mach[\component]\) from state elements to values, and may also contain additional
security state. For convenience, we abbreviate
multiple updates \(m[\component_0 \mapsto \word_0][\component_1 \mapsto \word_1]\dots\)
as \(m \llbracket A \mapsto B | C \rrbracket\), where \(A\) and \(B\)
are fomulae with free variables bound to sets in \(C\).
The base machine step function
\(\mach \stepstounder{} \mach' \in \MACHS \rightharpoonup \MACHS\) represents a single step.
It is partial to represent the capacity of the machine to failstop.
In order to accommodate failstop behavior, our properties will be {\it termination insensitive}.

The set of instructions, \(I \subseteq \WORDS\), corresponds to the RISC-V ISA.
We further introduce {\it macro-instructions}: sequences of
instructions that operate as if they were single, atomic pseudoinstructions.
A macro-instruction consists of both a list
of instructions and a pseudoinstruction that identifies its purpose in the
property. The pseudoinstructions, and the data that they carry, are as follows.

\begin{align*}
\psi \in \Psi ::= & \mathbf{call} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{tailcall} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{return} & \\
| & \mathbf{alloc} ~ size & size \in \mathbb{N} \\
| & \mathbf{setex} ~ \addr_{buf} \\
| & \mathbf{throwex} ~ \addr_{buf} \\
\end{align*}

An macro-instruction \((\bar{i},\psi) \in J\) is a pair of a pseudoinstruction and
a non-empty list of instructions. In order to implement the atomic nature of
executing macro-instructions,
we define a {\it ranged-step} relation that, given a pair of addresses
\(a_{low}\) and \(a_{high}\), steps as long the program counter is between them.

\judgment[Done]
         {\(\mach[\PCname] < a_{low} \lor \mach[\PCname] > a_{high}\)}
         {\(a_{low},a_{high} \vdash \mach \manystepstounder{} \mach\)}

\judgmenttwobrlong[Step]
                  {\(a_{low} \leq \mach[\PCname] < a_{high}\)}
                  {\(\mach \stepstounder{} \mach'\)}
                  {\(a_{low},a_{high} \vdash \mach' \manystepstounder{} \mach''\)}
                  {\(a_{low},a_{high} \vdash \mach \manystepstounder{} \mach''\)}

Now we're ready to introduce the overlay semantics.
Additionally, we keep track of security context information
specific to each stack over the course of the run.
This data is not relevant to execution,
it is only used to define the stack safety property. We define a set of
{\it security classes}:
\[sc \in SEC ::= \public | \sealed | \unsealed\]
A {\it security view} \(V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\) divides the machine
elements in terms of their purpose relative to the active function.
The {\it initial view} \(V_0\) maps all stack locations and non-public registers
to \(\unsealed\) and all other locations and public registers to \(\public\).
A set of {\it targets} identify the addresses of the program counter or
stack pointer at a return point:
\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_{pc} ~ a_{sp} \\
& \mathit{Catch} ~ a_{buf} ~ a_{pc} ~ a_{sp} \\
& \mathit{Done} \\
\end{split}\]
And a {\it stack context} is a non-empty stack of pairs of targets and views:
\[\context \in \CONTEXTS ::= \mathit{list} ~ (\mathit{TAR} \times \mathit{VIEW})\]

The initial stack context \(\context_0\) is \(\left[ (\mathit{Done}, V_0) \right]\).

An {\it overlay state} \(\sigma\) consists of a pair of a machine state
and a stack contexts.
\[\sigma = (\mach, \context) \in \mathcal{S} ::= \MACHS \times \CONTEXTS\]

The labeled step function for overlay states
\(\sigma \stepstounder{\psi?} \sigma' \in
\mathcal{S} \rightarrow  (\Psi + \bot) \times \mathcal{S}\)
proceeds by an {\it overlay step}
if the program counter points to the start of a macro-instruction's instruction sequence.
Otherwise, it proceeds by the default step. The definitions of context steps
\(\constep{\psi} \in \MACHS \times \CONTEXTS \times \Psi \rightarrow \CONTEXTS\)
will be defined for each pseudoinstruction as we introduce new topics.

\judgmentthreebrlong[Overlay]
                    {\((\bar{i}, \psi) \in J\)}
                    {\(\mach',\context \constep{\psi} \context'\)}
                    {\(\mach \manystepstounder{} \mach'\)}
                    {\(\mach[\PCname+n] = \bar{i}[n]\) for each \(n\) where \(0 \leq n < |\bar{i}|\)}
                    {\((\mach,\context) \stepstounder{\psi} (\mach',\context')\)}

\judgment[Default]
         {\(\mach \stepstounder{} \mach'\)}
         {\((\mach,\context) \stepstounder{\bot} (\mach',\context)\)}

\paragraph*{Macro-instruction definitions}

[TBD]

Note that there can be multiple macro-instructions with different instructions
that represent the same pseudoinstruction.
[This is less likely when we have smaller pseudoinstructions.]

\paragraph*{Events and Traces}

@@

A {\em trace} is a nonempty, finite or infinite sequence
of pairs of processors and events, ranged over by \(\obsT\).
We use ``\(\notfinished{}{}\)'' to represent ``cons'' for traces, reserving ``::''
for list-cons.

@@

We write that execution from a state produces an observation trace \(\sigma \hookrightarrow \obsT\)
as follows, coinductively:

@@

We define another relation that takes a trace of a callee up to its return, or until
an exception is thrown, if either occurs.
We write this \(\context' \downarrow (\mach,\context) \hookrightarrow \obsT\), where \(\context\)
is the context of the caller.

@@

%\begin{minipage}{.4\columnwidth}
%  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
%           {\(\notfinished{(\rho',\obs)}{\obsT_1} \eqsim_\rho \obsT_2\)}
%\end{minipage}
%\begin{minipage}{.4\columnwidth}
%  \judgment{\(\obsT_1 \eqsim_\rho \obsT_2\)}
%           {\(\obsT_1 \eqsim_\rho \notfinished{(\rho',\obs)}{\obsT_2}\)}
%\end{minipage}

\section{Stack Safety With Calls and Returns}

In this section we will present the context steps for calls and returns,
and show how they translate into properties. They are given formally in
Figure \ref{fig:callcontexts}.

For calls, we define a function, {\it update view}, that defines the view
of a caller in terms of that of the callee.
First, all stack locations below the stack pointer
are \(\unsealed\) -- fair game for the callee to allocate or write to, and
to read after writing. All \(\unsealed\) locations above the stack pointer
become \(\sealed\) -- their contents are both secret to and protected
from the callee. Argument and system registers are automatically marked
\(\mathit{public}\). All other locations above the stack pointer
retain their prior status (these will only be \(\sealed\) for now,
until we introduce shareable allocations shortly.)

To update the context for a call, we pair the updated view with the return target of the
call and push it to the stack. The return target will tell us whether a future
return is to the proper location with the stack pointer restored.
The view tells us how to treat the security of the callee's state, and as
it becomes more complicated, will benefit from the history that we maintain.

On a return, we pop the topmost pair from the context that has
a \(\mathit{return}\), along with any other pairs (catch points,
for instance) that we pass.

\begin{figure*}
\[\begin{split}
& \mathit{update\_view} ~ V ~ a_{sp} ~ \overline{r_{args}} \triangleq
\lambda \component .
\begin{cases}
  \public & \textnormal{else if } \component \in \REGS \textnormal{ and }
  \component \in \overline{r_{args}} \textnormal{ or } \component \in \mathit{PUBLIC} \\
  \unsealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } \component \leq a_{sp} \\
  \unsealed & \textnormal{else if } \component \in \REGS \textnormal{ and } \component \in \mathit{CLR\_SV} \\
  \sealed & \textnormal{else if } \component \in \WORDS \textnormal{ and } a_{sp} < \component \textnormal { and } V ~ \component = \unsealed \\
  \sealed & \textnormal{else if } \component \in \REGS  \\
  V ~ \component & \textnormal{otherwise} \\
\end{cases} \\
\end{split}\]

\judgmenttwobrlong[CallC]
                  {\(\psi = \mathbf{call} ~ r_{target} ~ \overline{r_{args}}\)}
                  {\(T' = \mathit{Return} ~ (m[pc] + 4) ~ m[sp]\)}
                  {\(V' = \mathit{update\_view} ~ V ~ m[sp] ~ \overline{r_{args}}\)}
                  {\(\mach, (T,V)::\context \constep{\psi} (T',V')::\context\)}

\judgment[ReturnCRet]
         {\(\psi = \mathbf{return}\)}
         {\(\mach, (\mathit{return} ~ a_{pc} ~ a_{sp}, V)::\context \constep{\psi} \context\)}

\judgment[ReturnCDone]
         {\(\psi = \mathbf{return}\)}
         {\(m, [\mathit{Done},V] \constep{\psi} [\mathit{Done},V]\)}

\judgmenttwo[ReturnCSkip]
            {\(\psi = \mathbf{return}\)}
            {\(\mach, \context \constep{\psi} \context'\)}
            {\(\mach, (\_::\context) \constep{\psi} \context'\)}

@@

We start by defining a second-order logical operator
\(\context_{ret} \uparrow P\), read ``\(P\) holds on return to \(\context_{ret}\),''
where \(P\) is a predicate on machine states. This is a coinductive relation
similar to ``weak until'' in temporal logic -- it holds if the condition
is never reached.

\judgmenttwo[Returned]
            {\(P ~ (\mach,\context)\)}
            {\(|\context| \leq |\context_{ret}|\)}
            {\((\context_{ret} \uparrow P) ~ (\mach, \context)\)}

\judgmenttwobrlong[Step]
                  {\(|\context| > |\context_{ret}|\)}
                  {\((\mach, \context) \stepstounder{\psi?} (\mach', \context')\)}
                  {\((\context_{ret} \uparrow P) ~ (\mach', \context')\)}
                  {\((\context_{ret} \uparrow P) ~ (\mach, \context)\)}

Similarly, in {\it caller confidentiality}, we will want to compare future states,
so we give a binary equivalent, \(\context \Uparrow R\), so that
\((\mach,\context) ~ (\context'' \Uparrow R) ~ (\mach',\context')\) holds if \(R\) holds on the
first return states after \((\mach,\context)\) and \((\mach',\context')\).

\judgmentthree[Returned]
              {\((\mach,\context) ~ R ~ (\mach',\context')\)}
              {\(|\context| \leq |\context_{ret}|\)}
              {\(|\context'| \leq |\context_{ret}|\)}
              {\((\mach,\context) ~ (\context_{ret} \Uparrow R) ~ (\mach',\context')\)}

\judgmenttwobr[Left]
              {\(\context_1 > \context_{ret}\)}
              {\((\mach_1,\context_1) \stepstounder{\psi?} (\mach_1',\context_1')\)}
              {\(\context_2 > \context_{ret}\)}
              {\((\mach_1',\context_1') ~ (\context_{ret} \Uparrow R) ~ (\mach_2,\context_2)\)}
              {\((\mach_1,\context_1) ~ (\context_{ret} \Uparrow R) ~ (\mach_2,\context_2)\)}

\judgmenttwobr[Right]
              {\(\context_1 > \context_{ret}\)}
              {\((\mach_2,\context_2) \stepstounder{\psi?} (\mach_2',\context_2')\)}
              {\(\context_2 > \context_{ret}\)}
              {\((\mach_1,\context_1) ~ (\context_{ret} \Uparrow R) ~ (\mach_2',\context_2')\)}
              {\((\mach_1,\context_1) ~ (\context_{ret} \Uparrow R) ~ (\mach_2,\context_2)\)}

@@

\judgmentbr[AllocC]
           {\(\psi = \mathbf{alloc} ~ size\)}
           {\(V' = V\llbracket m[sp]+i \mapsto \public | 0 < i \leq size \rrbracket\)}
           {\((\mach, (T,V)::\context) \constep{\psi} (T,V')::\context\)}

>>>>

We begin with a RISC-V-like machine enhanced with PIPE, a tag-based reference
monitor. We extend this machine with a {\it security overlay semantics},
which divides a program into dynamic {\it principals} that ought to be
protected from one another, and specifies that protection over a set
of abstract {\it overlay operations}. Specifications may take the form of
predicates on future states: statements of the form,
``When control returns to me...'', or of relations on traces of future execution
(hyper-properties.)

As opposed to a fully-abstract overlay semantics, in which overlay operations
are given safe-by-construction semantics then proven fully abstract,
our machine is not safe unless the monitor is correctly instantiated;
the overlay gives us the means to distinguish a monitor that implements
stack safety from one that does not.

The underlying machine is a standard RISC-V ISA as modeled in [MIT-RISCV].
Our overlay semantics provide overlay operations for the following code features:
\begin{itemize}
\item Function calls and returns, with caller- and callee-saved registers according
  to the RISC-V ABI
\item Arguments passed by reference
\item Exceptions
\item Tail-call Elimination
\end{itemize}

@@

\subsection{Security Overlay Semantics}

A security overlay semantics divides a program's execution into principals,
in this case function activations, and identifies which principal is active
in a given state. Overlay operations can generate new principals, transition
which principal is active, and allocate stack objects belonging to the active
principal. From this information, we derive the specifications that make up
stack safety. Specifications may take the form of predicates on
future states: statements of the form, ``When control returns to me...'',
or of relations on traces of future execution (hyper-properties.)

What this means in practice is that the compiler that generates a piece of
code must identify some instructions as implementing the overlay operations.
In the likely event that the operation requires multiple instructions,
typically the {\it last} instruction will be labeled.

Let \(\Psi\) be the set of overlay operations ranged over by \(\psi\).
We begin with the base machine, whose states are drawn from a set \(\mathcal{M}\),
and which transitions via partial step function \(\rightharpoonup\).
We define the operation \(m[k]\) as accessing the word in register
or at address \(k\) in state \(m\). The compiler provides a partial map
\(\mathit{over} \in \mathcal{W} \rightharpoonup \Psi\).
We lift \(\rightharpoonup\) into a labeled transition
\(\harpoonunder{\psi?} \in \mathcal{M} \rightharpoonup
\mathcal{M} \times (\Psi + \bot)\) by labeling each
transition \(\mach \harpoonunder{\psi?} \mach'\) where
\(\psi = \mathit{over} ~ \mach[\PCname]\) if it is defined and \(\bot\) if not.

\paragraph{Starting Overlay Operations in the Middle}

The concrete implementation of an overlay operation might contain multiple instructions,
and its security guarantees may not hold if they are executed out of order.
In fact, they almost certainly will not! But only one instruction is labeled.
It is the responsibility of the monitor to guarantee that this instruction is
executed at the appropriate place in its sequence.

\paragraph{The Compiler's Responsibility}

The code that is acted on by a security overlay semantics is precisely that code
that the compiler provides, down to any instruction tags that are needed to enforce
the associated micro-policy. The compiler is also responsible for labeling overlay
operations as such. This puts the burden on the compiler to be aware
of the available overlay operations and use them intentionally. We give a
concrete example of one such labeling scheme in [Testing Section.]

\subsection{The Basic Machine}

@@

Collectively addresses and registers are {\em state elements} \(\component\)
in the set \(\COMPONENTS ::= \WORDS + \REGS\).
%
A {\em machine state} \(\mach \in \MACHS\) is a type that exposes a mapping
\(\mach[\component]\) from state elements to values, and may also contain additional
security state. For convenience, we abbreviate
multiple updates \(m[\component_0 \mapsto \word_0][\component_1 \mapsto \word_1]\dots\)
as \(m \llbracket A \mapsto B | C \rrbracket\), where \(A\) and \(B\)
are fomulae with free variables bound to sets in \(C\).
The base machine step function
\(\mach \stepstounder{\psi?} \mach' \in \MACHS \rightharpoonup \MACHS\) is partial to
represent the capacity of the machine to failstop, and may be labeled with an overlay
operation.
In order to accommodate failstop behavior, our properties will be {\it termination insensitive}.

\subsection{Overlay Operations, Principals, and Overlay State}

Overlay operations are drawn from a set \(\Psi\), as follows:

\begin{align*}
\psi \in \Psi ::= & \mathbf{call} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{tailcall} ~ \reg_{target} ~ \overline{\reg_{args}} & \\
| & \mathbf{return} & \\
| & \mathbf{setex} ~ \addr_{buf} \\
| & \mathbf{throwex} ~ \addr_{buf} \\
| & \mathbf{alloc} ~ sizes & sizes \in \mathit{list} ~ \mathbb{N} \\
\end{align*}

Calls and tailcalls identify the target of the call, and the argument registers.
[Still a todo: stack arguments.] Return needs no further information. The operations
that setup and then throw to an exception handler take the address at which it is
stored. Alloc takes a list of sizes of objects to be allocated, because if allocating
objects means simply moving the function pointer, multiple
objects may be allocated at once.

Principals are function activations \(\alpha \in A\), with an operation
\(\mathit{fresh}\) that always generates a unique \(\alpha\).
Overlay state consists of a context stack, which contains the security-relevant
information associated with the active principal, and with inactive principals
waiting for control to return to them.

We define a set of {\it security classes}:
\[sc \in SEC ::= \public | \sealed | \unsealed | \mathit{object}\]

These indicate, from the perspective of the active principal, whether an element is
always accessible (\(\public\)), claimed by an inactive principal (\(\sealed\)),
available to be allocated and later sealed (\(\unsealed\)), or allocated by
the active principal (\(\mathit{object}\)).

A {\it security view} \(V \in \mathit{VIEW} ::= \COMPONENTS \rightarrow SEC\)
assigns each element a security class.

The {\it initial view} \(V_0\) maps all stack locations and non-public registers
to \(\unsealed\) and all other locations and public registers to \(\public\).

We additionally define a set of {\it targets}, which identify how a
principal expects to have control returned to it. This could be via a normal
return to the correct instruction \(\addr_{pc}\), or by catching the exception
whose state is saved at \(\addr_{buf}\). The \(\mathit{Active}\) target indicates
the active principal.

\[\begin{split}
tar \in TAR ::= & \mathit{Return} ~ a_{pc} \\
| & \mathit{Catch} ~ a_{buf} ~ a_{pc} \\
| & \mathit{Active} \\
\end{split}\]

Finally, a {\it context stack} is a non-empty stack of triples of an activation,
a target, and a view. The initial context stack \(\context_0 = (\mathit{fresh},\mathit{Active},V_0)\),
and the top target on the stack will always be \(\mathit{Active}\).
\[\context \in \CONTEXTS ::= \mathit{list} ~ (A \times \mathit{TAR} \times \mathit{VIEW})\]

We define an update function for context stacks indexed by an overlay operation.
This will be defined for each operation as we introduce them in detail.
\[\constep{\psi} \in \MACHS \times \CONTEXTS \times \Psi \rightarrow \CONTEXTS\]

From a machine state and a context stack, we create a {\it combined state} \((\mach,\context)\)
and a transition that steps the context according to the label on the transition,
if there is one, and otherwise maintains it.

\judgmenttwo[Overlay]
            {\(\mach \harpoonunder{\psi} \mach'\)}
            {\(\mach',\context \constep{\psi} \context'\)}
            {\((\mach,\context) \stepstounder{\psi} (\mach',\context')\)}

\judgment[Default]
         {\(\mach \harpoonunder{\bot} \mach'\)}
         {\((\mach,\context) \stepstounder{} (\mach',\context)\)}

\section{Context Updates With Calls and Returns}

In this section we will present the overlay steps for calls and returns.
They are given formally in Figure \ref{fig:callcontexts}.

In order to understand the motivation behind the call rule, though, we must first
describe how a function allocates objects. An allocation operation is parameterized
by a list of sizes; for each entry in the list, it marks an appropriate range
(based on offset from the stack pointer) as \(\mathit{object}\). This has no
direct bearing on the active principal, which may continue using the memory,
initialize it or not, and so on.

For calls, we define a function, {\it update view}, that defines the view
of a caller in terms of that of the callee. All argument registers are marked
\(\public\), along with all actual public registers. Callee-save registers,
including the stack pointer, are \(\sealed\); the callee is obligated to restore
them to their original value. The remaining caller-save registers are \(\unsealed\).

Then, all private objects are \(\sealed\), while the remainder of the stack retains
its old security context.

The formerly active principal is given a \(\mathit{Return}\) target, and on top of
it in the context stack we push a principal with a fresh identifier, the \(\mathit{Active}\)
target, and the updated view. On return, we search the stack for the first
\(\mathit{Return}\) target, and restore that principal to active status with its
original view. The rules given in Figure \ref{fig:callcontexts} take precedence
in order.

\begin{figure*}
  \judgment[AllocCNil]
           {\(\psi = \mathbf{alloc} ~ [ ~ ]\)}
           {\(\mach, \context \constep{\psi} \context\)}

  \judgmentthreebrtwo[AllocCCons]
                     {\(\psi = \mathbf{alloc} ~ s::sizes\)}
                     {\(\mach, (\alpha,T,V')::\context \constep{\psi'} \context'\)}
                     {\(b = \mach[sp] + sum(sizes)\)}
                     {\(\psi' = \mathbf{alloc} ~ sizes\)}
                     {\(V' = V\llbracket \addr \mapsto \mathit{object} | b \leq \addr < b+s \land V ~ \addr = \unsealed \rrbracket\)}
                     {\(\mach, (\alpha,T,V)::\context \constep{\psi} \context'\)}

  \[\mathit{reg\_view} ~ \overline{r_{args}} \triangleq \lambda \reg .
  \begin{cases}
    \public & \textnormal{if } \reg \in \overline{r_{args}} \textnormal{ or } \reg \in \mathit{PUBLIC} \\
    \unsealed & \textnormal{else if } \reg \in \mathit{CLR\_SV} \\
    \sealed & \textnormal{else} \\
  \end{cases}\]

  \[\mathit{update\_view} ~ V ~ \overline{r_{args}} \triangleq \lambda \component
  \begin{cases}
    \mathit{reg\_view} ~ \overline{r_{args}} ~ \component & \textnormal{if } \component \in \REGS \\
    \sealed & \textnormal{else if } V ~ \component = \mathit{object} ~ \mathbf{F} \\

      V ~ \component & \textnormal{otherwise} \\
  \end{cases}\]

  \judgmenttwobr[CallC]
              {\(\psi = \mathbf{call} ~ r_{target} ~ \overline{\reg_{args}}\)}
              {\(T = \mathit{Return} ~ (\mach[pc] + 4)\)}
              {\(V' = \mathit{update\_view} ~ V ~ \overline{\reg_{args}}\)}
              {\(\alpha' = \mathit{fresh}\)}
              {\(\mach, (\alpha,\mathit{Active},V)::\context \constep{\psi}
                (\alpha',\mathit{Active},V')::(\alpha,T,V)::\context\)}

  \judgmenttwo[ReturnCRet]
              {\(\psi = \mathbf{return}\)}
              {\(T = \mathit{Return} ~ \_\)}
              {\(\mach, (\_, \mathit{Active}, \_)::(\alpha, T, V)::\context
                \constep{\psi} (\alpha, \mathit{Active}, V)::\context\)}

  \judgmenttwo[ReturnCSkip]
              {\(\psi = \mathbf{return}\)}
              {\(\mach, \context \constep{\psi} \context'\)}
              {\(\mach, (\alpha, \mathit{Active}, V)::\_::\context
                \constep{\psi} (\alpha, \mathit{Active}, V)::\context\)}

  \judgment[ReturnCNoRet]
           {\(\psi = \mathbf{return}\)}
           {\(\mach, [(\alpha,\mathit{Active},V)] \constep{\psi}
             [(\alpha,\mathit{Active},V)]\)}

\subsection{Events and Traces}

@@

A {\em trace} is a nonempty, finite or infinite sequence
of events, ranged over by \(\obsT\).
We use ``\(\notfinished{}{}\)'' to represent ``cons'' for traces, reserving ``::''
for list-cons.

@@

We write that execution from a state produces an observation trace \(\mach,\context \hookrightarrow \obsT\)
as follows, coinductively:

@@

We define another relation that takes a trace of an activation until it is dead -- neither
active, nor inactive and waiting for return.
We write this \(\context' \downarrow (\mach,\context) \hookrightarrow \obsT\), where \(\context'\)
is the context of the caller.

@@

@@

We start by defining a second-order logical operator
\(\alpha \uparrow P\), read ``\(P\) holds on return to \(\alpha\),''
where \(P\) is a predicate on machine states. This is a coinductive relation
similar to ``weak until'' in temporal logic -- it holds if the condition
is never reached.

\judgment[Returned]
         {\(P ~ (\mach,(\alpha,T,V)::\context)\)}
         {\((\alpha \uparrow P) ~ (\mach, (\alpha,T,V)::\context)\)}

\judgmenttwobrlong[Step]
                  {\(\alpha \not = \alpha'\)}
                  {\((\alpha \uparrow P) ~ (\mach', \context')\)}
                  {\((\mach, (\alpha',T,V)::\context) \stepstounder{\psi?} (\mach', \context')\)}
                  {\((\alpha \uparrow P) ~ (\mach, (\alpha',T,V)::\context)\)}

Similarly, in {\it caller confidentiality}, we will want to compare future states,
so we give a binary equivalent, \(\alpha \Uparrow R\), so that
\((\mach,\context) ~ (\alpha \Uparrow R) ~ (\mach',\context')\) holds if \(R\) holds on the
first return states after \((\mach,\context)\) and \((\mach',\context')\).

\judgment[Returned]
         {\((\mach,(\alpha,T,V)::\context) ~ R ~ (\mach',(\alpha,T',V')::\context')\)}
         {\((\mach,(\alpha,T,V)::\context) ~ (\alpha \Uparrow R) ~ (\mach',(\alpha,T',V')::\context')\)}

\judgmenttwobrlong[Left]
              {\(\alpha \not = \alpha'\)}
              {\((\mach_1',\context_1') ~ (\alpha \Uparrow R) ~ (\mach_2,\context_2)\)}
              {\((\mach_1,(\alpha',T,V)::\context_1) \stepstounder{\psi?} (\mach_1',\context_1')\)}
              {\((\mach_1,(\alpha',T,V)::\context_1) ~ (\alpha \Uparrow R) ~ (\mach_2,\context_2)\)}

\judgmenttwobrlong[Right]
              {\(\alpha \not = \alpha'\)}
              {\((\mach_1,\context_1) ~ (\alpha \Uparrow R) ~ (\mach_2',\context_2')\)}
              {\((\mach_2,(\alpha',T,V)::\context_2) \stepstounder{\psi?} (\mach_2',\context_2')\)}
              {\((\mach_1,\context_1) ~ (\alpha \Uparrow R) ~ (\mach_2,(\alpha',T,V)::\context_2)\)}

@@
